### 2015-07-15 thesis/thesis/chap6/chap6.tex
changes

As future work, for the community formation in our first model, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal
$\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications. From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperative game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.

For the distributed model, our future plan is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches. In fact, game theory provides powerful techniques for strategic decision making, particularly cooperative and coalition formation games. Hedonic games and fractional hedonic games are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members. We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will stay for long period. The SVM machine learning algorithm is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs. This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

>>>>

As future work, for the community formation in our first model, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal
$\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications. From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperative game theory concepts\cite{RePEc:roc:rocher:554} can be used to help web services resolve the instability and unfairness issues by side payments.

For the distributed model, our future plan is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches. Hedonic games and fractional hedonic games\cite{Brandl:2015:FHG:2772879.2773307, Aziz_GGMT_70} are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members. We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will last for long period. The SVM machine learning algorithm\cite{Osuna97trainingsupport, Cortes:1995:SN:218919.218929} is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs. This can further facilitate the process of finding optimal cooperators in which will result in enhancing web services' overall performance as service providers.
